Simulations of Ballot Polling Risk-Limiting Audits

### 2022-07-20 providence/sections/sims.tex
better plots

\begin{figure}
\includegraphics[width=.5\textwidth]{prov_risk.png}
\caption{The proportion of simulated audits with an underlying tie that stopped in one of the five simulated rounds.}
\label{fig:prov-risk}
\end{figure}

In the simulations with an underlying tie, the proportion of audits that stop, as shown in Figure~\ref{fig:prov-risk}, give an estimate of maximum risk. For all margins, this estimated risk is less than the risk limit, supporting the claim that \Providence is risk-limiting.

\begin{figure}
\includegraphics[width=.5\textwidth]{prov_sprob.png}
\caption{The proportion of simulated audits with an margin as announced that stopped in one of the five simulated rounds.}
\label{fig:prov-sprob}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=.5\textwidth]{prov_risk.png}
\caption{The percent of simulated audits \Providence with an underlying tie that stopped in any of the five simulated rounds. This percent gives an estimate of the risk of the \Providence.}
\label{fig:prov-risk}
\end{figure}

In the simulations with an underlying tie, the percent of audits that stop, as shown in Figure~\ref{fig:prov-risk}, give an estimate of maximum risk. For all margins, this estimated risk is less than the risk limit, supporting the claim that \Providence is risk-limiting.

\begin{figure}
\includegraphics[width=.5\textwidth]{prov_sprob.png}
\caption{For the simulated \Providence audits with underlying margin as announced, the percent of audits that stopped among those that entered a round. This percent gives an estimate of the stopping probability conditioned on the sample of the previous round. The average percent for rounds 1, 2, and 3 is $89.96\%$, $90.52\%$, and $90.98\%$ respectively. We show only the first three rounds since so few audits make it to rounds 4 and 5.}
\label{fig:prov-sprob}
\end{figure}

### 2022-07-20 providence/sections/workload.tex
notes
better plots

Consider the US state of Michigan. In the 2020 US Presidential contest, Michigan had a margin of $2.8\%$.

@@

We now consider a simple round schedule for our example. Each round is selected to give the same probability of stopping, $p$. If the audit does not stop in the first round, we find a round size which, given the sample drawn in the first round, will give a probability of stopping $p$ in the second round. For this round schedule scheme, a one-and-done audit is achieved by choosing large $p$, say $p=.9$ or $p=.95$. For this particular round schedule scheme, computing the expected number of rounds is possible analytically(TODO: I worked it out, just need to add here). Our simulations are then used to estimate the expected number of ballots.

@@

Without workload measurements from multiple round audits, it is difficult to know an accurate value for $c_r$, and so we also evaluate the simulation results with varying $c_r$. 
For each $c_r$, we find the value of $p$ which minimizes the expected workload as we did in Figure~\ref{fig:workload}. Rather than use the minimum cost estimate among the sparsely sampled points, we fit a quadratic polynomial and use its minimum to get a smoother relationship between $c_r$ and optimal $p$. Figure~\ref{fig:optimal_ps} presents, for varying $c_r$ the round schedule parameter $p$ which minimizes expected workload. 
We observe that for a workload model with no overhead for each round (i.e. $c_r=0$), the optimal round schedule is that with $p=0.72$. As $c_r$ increases, the optimal value of $p$ also increases, up to as much as $p=.9$ for $c_r=10^4$.

Analysis like this can be used to select round schedules for audits.

% check that report to see if we can at least suggest what might be reasonable

@@

>>>>

Consider the US state of Michigan. In the 2020 US Presidential contest, Michigan had a margin of $2.8\%$. We again use risk-limit $\alpha = .1$.

@@

We now consider a simple round schedule for our example. Each round is selected to give the same probability of stopping, $p$. If the audit does not stop in the first round, we find a round size which, given the sample drawn in the first round, will give a probability of stopping $p$ in the second round. For this round schedule scheme, a one-and-done audit is achieved by choosing large $p$, say $p=.9$ or $p=.95$. For this particular round schedule scheme, computing the expected number of rounds is possible analytically(TODO: I worked it out, just need to add here). Our simulations are then used to estimate the expected number of ballots.
We run $10^4$ trials for each value of $p$.

@@

Without workload measurements from multiple round audits, it is difficult to know an accurate value for $c_r$, and so we also evaluate the simulation results with varying $c_r$. 
For each $c_r$, we find the value of $p$ which minimizes the expected workload as we did in Figure~\ref{fig:workload}. Rather than use the minimum cost estimate among the sparsely sampled points, we fit a quadratic polynomial and use its minimum to get a smoother relationship between $c_r$ and optimal $p$. Figure~\ref{fig:optimal_ps} presents, for varying $c_r$ the round schedule parameter $p$ which minimizes expected workload. 
We observe that for a workload model with no overhead for each round (i.e. $c_r=0$), the optimal round schedule is that with $p=0.72$. As $c_r$ increases, the optimal value of $p$ also increases, up to as much as $p=.9$ for $c_r=10^4$.
(TODO: check report(s) for any bit of an estimate we can give of what these values might be in practice, noting the issues/error expected)

@@

Analysis like this may be useful to election officials for selecting round schedules for audits. 
It remains an open question whether a fast, accurate analytical approach for estimating $E_b$ and $E_r$ exists.

Since the simulations are relatively computationally expensive, an analytical alternative is desirable. (TODO: need to compare my best analytical approach to the simulation results now)
